What can we learn about life in the city by mining the Melbourne’s Open Data Platform?

### 2017-05-07 thesis/proposal_draft.Rmd
added more detailed caption to figure 2

\begin{center}
\textbf{Figure 2}: Smoothed pedestrian counts for Melbourne Central by day of the week and month of the year
\end{center}

>>>>

\begin{center}
\textbf{Figure 2}: Smoothed pedestrian counts for Melbourne Central by day of the week and month of the year. Month of the year is mapped to colour. We see that the daily patterns are quite consistent between days of the week, although we note that the amount of pedestrians at late hours of the day are higher during Friday and Saturday compared to other days.
\end{center}
